A Hitchhiker's Guide to Reproducible Research" # replace with something serious

### 2021-05-03 manuscript.Rmd
actually print hash
add introduction to "prepare public release"

@@

```{r}
system("git rev-parse --short HEAD")
```

@@

> Log into zenodo.org → Account → GitHub[^zenodo-github]

>>>>

An open research project usually entails that you publish content to the public web, without an intermediate publisher.
Since you are directly responsible for such content, you have to prepare a few things that are usually done by the publisher for you.

@@

```{r}
system2("git", c("rev-parse",  "--short",  "HEAD"), stdout = TRUE)
```

@@

> Log into zenodo.org → Account → [GitHub[^zenodo-github]](https://zenodo.org/account/settings/github/)
